Cloud Manufacturing Ecosystem - Scheduling And Evolving

### 2015-10-02 schedule.tex
start the schedule and evolve modules.

OAS

@@

\subsection{Service Standardization} % (fold)
\label{sub:service_standardization}

% subsection service_standardization (end)

@@

@@

\subsection{Matching Regulation} % (fold)
\label{sub:matching_regulation}

% subsection matching_regulation (end)

\subsection{Platform Assistance} % (fold)
\label{sub:platform_assistance}

% subsection platform_assistance (end)

\subsection{Service Dashboard} % (fold)
\label{sub:service_dashboard}

% subsection service_dashboard (end)
% section model (end)

>>>>

===================================

A scheduling methodology for production services is presented
by [59]. Order decomposition into tasks, the selection of one or several
service providers to perform them, and the scheduling of the whole
manufacturing process is considered. In [60], a resource scheduling
framework is proposed. On the basis of stochastic advanced Petri net,
queue balancing cutover (QBC) strategy is put forward as a solution to
the issue of request dispatching. The scheduling of collaborative
design tasks is described in [61], presenting a new immune genetic
algorithm. Improved searching diversity based on immune strategy, but
also adaptive adjustment for probabilities of crossover and mutation
with low time complexity are achieved with this concept.

==================================

@@

\subsection{Service Standardization} % (fold)
\label{sub:service_standardization}
Service standardization based mainly on  resource virtualization and encapsulation, where many models and methods were build on software and hardware like \cite{Li2011,Wu2011,Li2011a,Liu2011}. However, even if these resources were contrcuted into services with these models or methods, the difficulty of services scheduling changed slightly, for the absence of service standardization and similar type of services always turn out in different apperances.

Standardization is a process of Principal Component Analysis, like Guo et al.\cite{Guo2011} mined the correlation relationship of service composition in Cloud Manufacturing, we can use Online Learning\cite{Shalev-Shwartz2011} to mine out service prototypes and to refine them as case arrives by, where the sequential study cases are the continuous transactions.
% subsection service_standardization (end)

@@

OAS  
\begin{figure}[!h]
%\centering\small\resizebox{0.6\textwidth}{!}{\input{figures/order_flow}}
\caption{Primary Flow of Order}
\label{fig:orderflow}
\end{figure}

@@

\subsection{Matching Regulation} % (fold)
\label{sub:matching_regulation}
There are two main parts, recommendation for resource matching and resource prediction, of resources recommendation module that we will discuss in \autoref{sub:recommand_system}, and the first one depicted the situation where user in buyer role will always encounter.

In order to recommand poper manufacturing service with the order user submitted, service search engine should adopt a series of well designed matching regulations. Platform will collect the hit or miss data that feeded back from user, to train the classifier.
% subsection matching_regulation (end)

\subsection{Platform Assistance} % (fold)
\label{sub:platform_assistance}
a guide for scheduling 
% subsection platform_assistance (end)

\subsection{Service Dashboard} % (fold)
\label{sub:service_dashboard}
a monitor
% subsection service_dashboard (end)
% section model (end)
